(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 ms.tex
stellar props stuff

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we employ the use of stellar models.
We first download the isochrone grids from the 2012 updated photometric
systems for the relevant bandpasses from the Dartmouth Stellar Evolution
Database \citep{Dotter08}.
We then interpolate the isochrones onto a grid uniformly spaced in
stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to
\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to
1000 pc).
In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
We then compare the expected apparent magnitudes to our observed photometry
to measure the likelihood of each grid point.
For each parameter, we then marginalize our likelihood over all other
parameters in order to estimate the value of the physical properties
for each star.
\anytodo{This was done using MCMC right? Did you interpolate the
\emph{likelihood function} or the \emph{model predictions}?}

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may under-predict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

>>>>

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we used the publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for stellar model grids.  
This software does trilinear interpolation in mass-age-\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

This enables a set of observed properties ($\left\{ x_i, \sigma_i \right\}$), 
either spectroscopic, photometric, 
or both, to define a likelihood function that may be sampled in
an MCMC chain:
\begin{equation}
\label{eq:ischochronelhood}
\ln \mathcal L(\boldsymbol{\theta}) = -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i - 
  I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
\end{equation}
where $I_i(\boldsymbol{\theta})$ is the isochrone model prediction of property 
$i$ at the given parameters $\boldsymbol{\theta}$.  
If the observed properties include any apparent magnitudes, then 
$\boldsymbol{\theta}$ includes distance and $A_V$ extinction in addition 
to mass, age, and \feh.

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.  
We then run an MCMC chain using \texttt{emcee} \citep{Foreman-Mackey12}
for each host star conditioned on the observed 
photometric properties as presented in \ref{Table:photometry}, with 
the exception of the W4 band, which we leave out this analysis due to 
its unreliability.

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may under-predict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.

\anytodo{Is this paragraph necessary anymore?}
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.
